%-------------------------
% Resume in Latex
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Sushanth Suresh}} 
  & Email : \href{mailto:sushanthkengunte@gmail.com}{sushanthkengunte@gmail.com}\\
  Linkedin : \href{https://www.linkedin.com/in/sushanths/}{https://www.linkedin.com/in/sushanths/} 
  & Mobile : +1-315-515-2655 \\
  GitHub : \href{https://github.com/Sushanthkengunte}{https://github.com/Sushanthkengunte}
\end{tabular*}


%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Syracuse University}{Syracuse, NY}
      {Master of Science in Computer Science;  GPA: 3.63}{Aug. 2016 -- May. 2018}
    \resumeSubheading
      {Bangalore Institute of Technology}{Bangalore, India}
      {Bachelor of Engineering in Computer Science;  GPA: 3.70 (7.5/10.0)}{Aug. 2011 -- June. 2015}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Sam's club}{Bentonville, AR}
      {Software Engineer - II}{Sep 2018 - Present}
      \resumeItemListStart
       \resumeItem{Description}
        {As an integral part of a large critical system the Warehouse Management system, I have proactively taken up various responsibilities as required by the team and delivered in time throughout the life cycle of the project.}\\
        \resumeItem{Back end developer}
            {Built the components using JAVA and tested using Junit4.Deployed using CI/CD pipelines linked to GitHub as the Version Control System. Deployed to azure kubernetes and Unix virtual machines using active-passive approach to maintain high availability.}\\
            \resumeItemListStart
                \resumeItem{Web Services}
                    {Owned and built the component responsible to re-process the messages if needed when the normal flow stopped and archive all the messages coming into the system. Built Rest services to trigger the re-processing jobs.}\\
                \resumeItem{PAAS developer}
                    {Build a workflows that pols the azure blob, azure service bus,outlook accounts for new messages. Process them using xslt transformation, azure functions. Passing it to another service bus or create a slack message.}\\
                \resumeItem{Kafka Consumer}
                     {Built a spring boot component that filtered out 827 relevant messages from 10000+ messages and further putting into a service bus.}\\
            \resumeItemListEnd
        \resumeItem{Partitioning, Scaling and high availability}
          {Incorporated load balancer to the Rest Services components deployed in two regions using active-passive approach.}\\
        \resumeItem{Telemetry}
          {Led the effort to incorporate azure application insights as the logging mechanism in all the components built and deployed, by developing a proof of concept and documenting the steps to incorporating it in spring boot application and azure functions.}\\
        \resumeItem{Design}
          {Drove the conversation while analysing the different options provided as the source of information; concluding on the specific Kafka topics to be for our use case.}\\
        \resumeItem{Requirement Gathering}
          {Procured information about a component and set up a base understanding with the stakeholders by assimilating the different nomenclatures,contexts refereed by different teams.}\\
        \resumeItem{Front End developer}
          {Persuaded the team to create a user interface by giving a proof of concept of a landing page and a transitioning to display the purchase orders using ReactJS.}
      \resumeItemListEnd

    \resumeSubheading
      {Syracuse University }{Syracuse, NY}
      {Research Assistant}{Sep 2017 - Sep 2018}
      \resumeItemListStart
        \resumeItem{Description}
          {Predicted TODO:<Percentage got> drop in the viewership drop during commercial breaks by applying learning algorithms using Python.}
        \resumeItem{Method}
          {Explored the different algorithms by taking and comparing data provided by ComScore TV Essentials for few popular TV shows such as Big Bang Theory,TODO: <Fill in TV shows>}
        \resumeItem{Factors used}
            {TODO:<Fill the factors used>}
      \resumeItemListEnd

    \resumeSubheading
      {Accenture Service pvt Ltd}{Bangalore, India}
      {Associate Software Engineer}{Nov 2015 - Jul 2016}
      \resumeItemListStart
        \resumeItem{Training}
          {Developed a event management tool using JAVA,Spring, Maven, Hibernate, J2EE, MySQL; Bolstering the knowledge about Bean-factory, Bean-Injection, Java-Servlet Pages, Tomcat Apache Server and Unit-Testing.}
        \resumeItem{Endur}
          {Reliably updated and maintained the server configurations using a book keeping tool.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Log-Structured File System}
      {Increased the performance of the file system by incorporating log-structure, indexing and cleaning policy to an Unix style file system.}
    \resumeSubItem{Kernel level programs}
      {Implemented the operating system programs such as fork, exec,exit,paging and Memory visualization.}
    \resumeSubItem{Type based compiler}
      {Built a type based compiler to understand the dependencies of source files.}
    \resumeSubItem{Yelp Camp}
      {Designed and developed a full stack website to view and manage the various campground and providing basic CRUD operations for the campground.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
%\section{Programming Skills}
%  \resumeSubHeadingListStart
%    \item{
%      \textbf{Languages}{: Scala, Python, Javascript, C++, SQL, Java}
%      \hfill
%      \textbf{Technologies}{: AWS, Play, React, Kafka, GCE}
%    }
%  \resumeSubHeadingListEnd


%-------------------------------------------
\end{document}
